---
title: "Regression"
author: "Mohammad Pourabbasian"
date: "2025-03-24"
output: html_document
---
```{r setup}
library(pwr)
library(broom)
library(see)
library(performance)
library(report)
library(tidyverse)
stars <- read_csv("L3_stars.csv")
engage <- read_csv("psess.csv")
```
```{r T2}
#Tidy the data
stars2 <- stars %>% pivot_longer(cols = Q01:Q51,
                                 names_to = "Question",
                                 values_to = "Score") %>% arrange(ID)

```
```{r T3}
#Calculating mean anxiety score
stars_means <- stars2 %>%
  group_by(ID) %>%
  summarise(mean_anxiety = mean(Score, na.rm = TRUE))
```

```{r T4}
# join engage and stars
joined <- inner_join(stars_means,engage,  by = "ID") 
```

```{r T5}
#Calculate descriptives for the variables overall
descriptives <- joined %>%
  summarise(mean_anx = mean(mean_anxiety, na.rm = TRUE),
            sd_anx = sd(mean_anxiety, na.rm = TRUE),
            mean_weeks = mean(n_weeks, na.rm = TRUE),
            sd_weeks = sd(n_weeks, na.rm = TRUE))

```

```{r T6}
#visualisation 

joined %>% ggplot(aes(x = mean_anxiety, y = n_weeks)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme_bw()
```

```{r T7}
#Running the regression
mod <- lm(n_weeks ~ mean_anxiety, joined)
mod_summary <- summary(mod)
```
```{r T8}
#Assumption check
check_model(mod)
check_normality(mod)
check_heteroscedasticity(mod)

```
```{r T9}
#Power and effect size
##calculate the minimum effect size
pwr.f2.test(u = 1, v = 35, f2 = NULL, sig.level = .05, power = .8)
##calculate observed effect size(f2)
f2 <- mod_summary$adj.r.squared/(1- mod_summary$adj.r.squared)

```

```{r T10}
#Write-up
##manually calculating p-value for inline code
f <- mod_summary$fstatistic
mod_p <- pf(f[1], f[2], f[3], lower = FALSE)

##Write-up using report
report(mod)

```

#Inline Report  

A simple linear regression was performed with engagement (M = `r descriptives$mean_weeks %>% round(2)`, SD = `r descriptives$sd_anx %>% round(2)`) as the outcome variable and statistics anxiety (M = `r descriptives$mean_anx %>% round(2)`, SD = `r descriptives$sd_anx %>% round(2)`) as the predictor variable. The results of the regression indicated that the model significantly predicted course engagement (F(`r mod_summary$fstatistic[2]`, `r mod_summary$fstatistic[3]`) = `r mod_summary$fstatistic[1] %>% round(2)`, p < .001, Adjusted R2 = `r mod_summary$adj.r.squared %>% round(2)`, f2 = .63), accounting for `r (mod_summary$adj.r.squared %>% round(2))*100`% of the variance. Anxiety was a significant predictor (b = `r mod$coefficients[2] %>% round(2)`, p < `r mod_p %>% round(3)`.
)
```{r}

```


 


