---
title: "Multiple Regression"
author: "Mohammad Pourabbasian"
date: "2025-03-26"
output: html_document
---
```{r}
#setup
library(pwr)
library(see)
library(performance)
library(report)
library(tidyverse)
pinfo <- read_csv("participant_info.csv")
wellbeing <- read_csv("wellbeing.csv")
screen <- read_csv("screen_time.csv")
```
```{r T3}
#Calculating wellbeing score
wemwbs <- wellbeing %>% pivot_longer(names_to = "Scale",
                                     values_to = "Score",
                                     -Serial) %>% 
  group_by(Serial) %>%
  summarise(tot_wellbeing = sum(Score))
wemwbs %>% summarise(mean = mean(tot_wellbeing),
                             sd = sd(tot_wellbeing),
                             min = min(tot_wellbeing),
                             max = max(tot_wellbeing))
#Visulasing distribution
wemwbs %>% ggplot(aes(x = tot_wellbeing))  +
  geom_histogram() + 
  theme_bw()

```

```{r}
#visualise the relationship
screen_long <- screen %>%
  pivot_longer(names_to = "var", values_to = "hours", -Serial) %>%
  separate(var, c("variable", "day"), "_")
screen2 <- screen_long %>%
  mutate(variable = dplyr::recode(variable,
               "Watch" = "Watching TV",
               "Comp" = "Playing Video Games",
               "Comph" = "Using Computers",
               "Smart" = "Using Smartphone"),
     day = dplyr::recode(day,
              "wk" = "Weekday",
              "we" = "Weekend"))
dat_means <- inner_join(wemwbs, screen2, "Serial") %>%
  group_by(variable, day, hours) %>%
  summarise(mean_wellbeing = mean(tot_wellbeing))
ggplot(dat_means, aes(hours, mean_wellbeing, linetype = day)) +
  geom_line() +
  geom_point() +
  facet_wrap(~variable, nrow = 2)
```
```{r}
#Smartphone and well-being for boys and girls
smarttot <- screen2 %>% filter(variable == "Using Smartphone") %>%
  group_by(Serial) %>%
  summarise(tothours = mean(hours))
smart_wb <- smarttot %>% filter(tothours > 1.00) %>%
  inner_join(y = wemwbs, "Serial") %>% inner_join(y = pinfo, "Serial")


```

```{r}
#Mean-centering variables
smart_wb <- smart_wb %>% mutate(thours_c = (tothours - mean(tothours)),
                                  male_c = if_else(male == 1, .5, -.5),
                                male_c = as.factor(male_c),
                                male = as.factor(male)) 
```

```{r}
#Visualise the relationship
desc <- smart_wb %>% group_by(tothours, male_c) %>%
  summarise(mean = mean(tot_wellbeing))
desc %>% 
  ggplot(aes(x = tothours, y = mean, color = male_c)) +
  geom_point() + 
  geom_smooth(method = "lm", alpha = .25) +
  labs(x = "Total hours samrtphone use",
       y = "Mean well-being score",
       color = "Gender") +
  scale_color_hue(labels = c("Female", "Male")) +
  theme_bw()
  
  
```

## Interpretation  

Girls show lower overall well-being compared to boys.The data shows that longer smartphone use in boys and girls is associated with lower well-being. However, girls are more susceptible and each unit of smartphone use are associated more with a decrease in well-being scores in girls compared to boys. 

```{r}
#Running Regression
mod <- lm(tot_wellbeing ~ thours_c + male_c + thours_c*male_c, data = smart_wb)
mod_summary <- mod %>% summary()
```
## interpretation

smartphone use was more negatively associated with wellbeing for girls than for boys

```{r}
#Assumption Check
assumptions <- check_model(mod, check = c("vif", "qq", "normality", "linearity", "homogeneity"))
assumptions
check_normality(mod) #big data set sensitivity
check_homogeneity(mod)
check_collinearity(mod)
```
## Problem with homogeneity plot  
For assumption 7, homoscedasticity, the plot is missing the reference line. The reason the line isn't there is because the dataset is so large that is creates a memory issue so we need to create the plot ourselves using code the developers of the package see provided to us on Twitter. The default code would try to draw confidence intervals around the line which is what causes the memory issue, this code removes that with se = FALSE.

```{r}
##Adjusted plot for homogeneity
ggplot(assumptions$HOMOGENEITY, aes(x, y)) +
    geom_point2() +
    stat_smooth(
      method = "loess",
      se = FALSE,
      formula = y ~ x,
    ) +
    labs(
      title = "Homogeneity of Variance",
      subtitle = "Reference line should be flat and horizontal",
      y = expression(sqrt("|Std. residuals|")),
      x = "Fitted values"
    ) 

```

```{r}
#Power and effect size
pwr.f2.test(u = 3, v = 71029, f2 = NULL, sig.level = .05, power = .99)

```

```{r}
#Prediction
newdata <- tibble(male_c = -.5, thours_c = 4) %>% mutate(male_c = as.factor(male_c))
predict(mod, newdata)
```
##Report  

All continuous predictors were mean-centered and deviation coding was used for categorical predictors. The results of the regression indicated that the model significantly predicted course engagement (F(`r mod_summary$fstatistic[2]`, `r mod_summary$fstatistic[3] %>% round(2)`) = `r mod_summary$fstatistic[1] %>% round(2)`, p < .001, Adjusted R2 = `r mod_summary$adj.r.squared %>% round(2)`, f^2^ = .63), accounting for `r (mod_summary$adj.r.squared %>% round(2))*100`% of the variance. Total screen time was a significant negative predictor of wellbeing scores (b = `r mod$coefficients[2] %>% round(2)`, p < .001, as was gender (b = `r mod$coefficients[3] %>% round(2)`, p < .001, with girls having lower wellbeing scores than boys. Importantly, there was a significant interaction between screentime and gender (b = `r mod$coefficients[4] %>% round(2)`, p < .001), smartphone use was more negatively associated with wellbeing for girls than for boys. 

```{r}
#
report(mod)
```

