---
title: "Ch2_PracticeSkills"
author: "Mohammad Pourabbasian"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


## Load in the data


```{r libraries, echo = FALSE, warning=FALSE, message=FALSE}
library("tidyverse")

screening <- read_csv("p_screen.csv")
responses <- read_csv("QHC_responses.csv")
scoring <- read_csv("QHC_scoring.csv")
```


### Task 1 - Oldest Participant

Replace the `NULL` in the `T1` code chunk with the Participant ID of the oldest participant. Store this single value in `oldest_participant`.


```{r T1}
oldest_participant <- screening %>%
  filter(AGE == max(AGE)) %>%
  pull(ID)
```

### Task 2 - Arranging D-SPAN

Replace the `NULL` in the `T2` code chunk with code that arranges participants' D-SPAN performance from highest to lowest using the appropriate one-table dplyr (i.e., Wickham) verb. Store the output in `cogtest_sort`. 


```{r T2}
cogtest_sort <- screening %>%
  arrange(desc(DSPAN))
```

### Task 3 - Foreign Language Speakers

Replace the `NULL` in each of the two lines of code chunk `T3`, so that `descriptives` has a column called `n` that shows the number of participants that speak a foreign language and number of participants that do not speak a foreign language, and another column called `median_age` that shows the median age for those two groups. 


```{r T3}
screen_groups <- screening %>%
  group_by(FLANG)
descriptives <- screen_groups %>%
  summarise(n = n(),
            median_age = median(AGE))
```

### Task 4 - Creating Percentage MOCA scores

Replace the `NULL` in the `T4` code chunk with code using one of the dplyr verbs to add a new column called `MOCA_Perc` to the dataframe `screening` In this new column should be the `MOCA` scores coverted to percentages. The maximum achievable score on MOCA is `30` and percentages are calculated as `(participant score / max score) * 100`. Store this output in `screening`.


```{r T4}

screening <- screening %>%
  mutate(MOCA_Perc = (MOCA /max(MOCA) * 100))
```

### Task 5 - Remove the MOCA column

Now that we have our MoCA score expressed as a percentage `MOCA_Perc` we no longer need the raw scores held in `MOCA`. Replace the `NULL` in the `T5` code chunk using a one-table dplyr verb to keep all the columns of `screening`, with the same order, but without the `MOCA` column. Store this output in `screening`.

```{r T5}
screening <- screening %>%
  select(-MOCA)
```

### Task 6 - Gather the Responses together

Replace the `NULL` in the `T6` code chunk using code to gather the responses to all the questions of the QHC from wide format to tidy/long format. Put the names in `Question` and the values in `RESPONSE`. Store this output in `responses_long`.


```{r T6}
responses_long <- responses %>% 
  pivot_longer(cols = Q1:Q15,
               names_to = "Question",
               values_to = "RESPONSE")
```

### Task 7 - Joining the data

Now we need to join the number of points for each response in `scoring` to the participants' responses in `responses_long`. 


```{r T7}
responses_points <- inner_join(responses_long, scoring, by = "RESPONSE")
```

### Task 8 - Working the Pipes

Below we have given you five lines of code that takes the data in its current long format and then creates a QHC score for each participant (`group_by()...summarise()`). It then joins the screening information (`inner_join()`) before calculating a mean QHC score for the two groups of participants - those that play musical instruments and those that don't. This final step is stored as a tibble called `musical_means`.  

``` {r T8}
participant_groups <- group_by(responses_points, ID)
participant_scores <- summarise(participant_groups, Total_QHC = sum(SCORE))
participant_screening <- inner_join(participant_scores, screening, "ID")
screening_groups_new <- group_by(participant_screening, MUSICAL)
musical_means <- summarise(screening_groups_new, mean_score = mean(Total_QHC))
```

Use the above five lines of code to replace the `NULL` in the `T8` code chunk with a functioning code pipeline using pipes. Put each function on a new line one under the other. This pipeline should result in the mean QHC values of musical and non-musical people being stored in the tibble `musical_means`. This final tibble will consist of two rows by two columns.  


```{r T8}
musical_means <- responses_points %>% 
  group_by(ID) %>%
  summarise(Total_QHC = sum(SCORE)) %>%
  inner_join(screening, "ID") %>%
  group_by(MUSICAL) %>%
  summarise(mean_score = mean(Total_QHC))
```

### Task 9 - Difference in Musical Means

Finally, replace the `NULL` in the `T9` code chunk with the value of how much higher the QHC score of people who play music is compared to people who don't play music. This should be a single numeric value, to two decimal places, e.g. 2.93

```{r T9}
QHC_diff <- musical_means %>% 
  summarise(dif = max(mean_score) - min(mean_score)) %>%
  pull(dif) %>%
  round(2)
```

