---
title: "Ch5_PracticeSkills.Rmd"
author: "Mohammad Pourabbasian"
output: html_document
---

This activity uses open data from Experiment 1 of <a href="https://journals.sagepub.com/stoken/default+domain/d5HcBHg85XamSXGdYqYN/full" target = "_blank">Mehr, Song, and Spelke (2016)</a>. This exercise is taken from the <a href="https://sites.google.com/view/openstatslab/home?authuser=0" target = "_blank">Open Stats Lab at Trinity University, US</a>.
 

### Does Music Convey Social Information to Infants? 

Parents often sing to their children and, even as infants, children listen to and look at their parents while they are singing. Research by Mehr, Song, and Spelke (2016) sought to explore the psychological function that music has for parents and infants, by examining the hypothesis that particular melodies convey important social information to infants. Specifically, melodies convey information about social affiliation.

The authors argue that melodies are shared within social groups. Whereas children growing up in one
culture may be exposed to certain songs as infants (e.g., “Rock-a-bye Baby”), children growing up in
other cultures (or even other groups within a culture) may be exposed to different songs. Thus, when a novel person (someone who the infant has never seen before) sings a familiar song, it may signal to the infant that this new person is a member of their social group.

To test this hypothesis, the researchers recruited 32 infants and their parents to complete an
experiment. During their first visit to the lab, the parents were taught a new lullaby (one that neither they nor their infants had heard before). The experimenters asked the parents to sing the new lullaby to their child every day for the next 1-2 weeks.

Following this 1-2 week exposure period, the parents and their infant returned to the lab to complete
the experimental portion of the study. Infants were first shown a screen with side-by-side videos of
two unfamiliar people, each of whom were silently smiling and looking at the infant. The researchers
recorded the looking behavior (or gaze) of the infants during this ‘baseline’ phase. Next, one by one, the two unfamiliar people on the screen sang either the lullaby that the parents learned or a different lullaby (that had the same lyrics and rhythm, but a different melody). Finally, the infants saw the same silent video used at baseline, and the researchers again recorded the looking behavior of the infants during this ‘test’ phase. For more details on the experiment’s methods, please refer to Mehr et al. (2016) Experiment 1.

For the exercise here we will be looking at the baseline data and test trial data for gazing proportion specifically.



### Load in the data

Call `tidyverse` to the `library()` and load in the data (`socialmelodies_exp1.csv`) and store them in object `melodydata`.

```{r T0}
library("tidyverse")

melodydata <- read_csv("socialmelodies_exp1.csv")
```


### Task 1 - Filter data

This data file includes the variables for all 5 experiments reported in the paper. We only want
to analyze the data for Experiment 1. Using the `filter()` function, create a new data frame `melodydata_exp1` that only contains data of Experiment 1 (variable `exp1` with value 1 indicates all data fro Experiment 1). 

```{r T1}
melodydata_exp1 <- melodydata %>% filter(exp1 == 1)
```

### Task 2 - Select data

As noted above, we will not be using all variables from `melodydata_exp1` and in order to get a better overview of the variables we are particularly interested in, we want to create an object that only contains the variables we are focusing on here.

Some context:
* First, you want to show that infants' looking behavior did not differ from chance during the
baseline trial (`Baseline_Proportion_Gaze_to_Singer`). In other words, the infants did not show an attentional bias prior to hearing the unfamiliar others sign the song. 
* Second, you want to examine whether the proportion of infants' looking
behaviour toward the singer of the familiar melody (`Test_Proportion_Gaze_to_Singer`) was higher than chance at the test phase.

Thus, create a new data frame called `melodydata_exp1_reduced` that only contains the variables `id`, `Baseline_Proportion_Gaze_to_Singer`, and `Test_Proportion_Gaze_to_Singer`. 

```{r T2}
melodydata_exp1_reduced <- melodydata_exp1 %>% select(id, Baseline_Proportion_Gaze_to_Singer, Test_Proportion_Gaze_to_Singer)
```


### Task 3 - Testing baseline gazing proportion

Perform a One-sample t-test to examine whether the proportion of time spent looking at the person singing the familiar song at baseline did not differ from chance (0.5).


```{r T3}
t.test(pull(melodydata_exp1_reduced, Baseline_Proportion_Gaze_to_Singer ), mu = 0.5)
```

### Task 4 - Testing test trial gazing proportion

Now, perform a One-sample t-test to examine whether the proportion of infants' looking
behaviour toward the singer of the familiar melody was higher than chance at the test phase
(0.5).


```{r T4}
t.test(pull(melodydata_exp1_reduced, Test_Proportion_Gaze_to_Singer), mu = 0.5)
```

### Task 5 - Gathering data into a different format

We want to create a boxplot to depict the proportion of time infants spent looking at the singer of the familiar song at the baseline and test trials. However, before we can do that, we need to slightly change the format of our `melodydata_exp1_reduced` data frame: Because we need to represent the same cases (individuals) twice in the same figure, we need to reorganise the data so it has all of the gaze proportions as one variable (`Proportion`), but with a separate variable indicating whether it belongs to the baseline or test trial (`TrialType`). Put differently, each participant should be represented by two rows; one row with the baseline proportion and another row with the test trial proportion.

Store the new data frame in object `melodydata_exp1_wide`.


```{r T5}
melodydata_exp1_wide <- melodydata_exp1_reduced %>% 
  pivot_longer(cols = c("Baseline_Proportion_Gaze_to_Singer", "Test_Proportion_Gaze_to_Singer"),
               names_to = "TrialType",
               values_to = "Proportion")
```



### Task 6 - Visualise baseline and test trial data

Generate a boxplot to depict the proportion of time infants spent looking at the singer of the
familiar song at the baseline and test trials.


```{r T6}
ggplot(melodydata_exp1_wide, aes(x = TrialType, y = Proportion, fill = TrialType)) +
  geom_boxplot(alpha = 0.6, ) + 
  guides(fill = FALSE) + 
  labs(title = "Figure 1",
       y = "Proportion of Looking Toward Singer of Familiar Song") +
  theme_minimal() 



```

**Finished**
