---
title: "Paired_sample_t"
author: "Mohammad Pourabbasian"
date: "2025-02-25"
output: html_document
---

```{r T1}
library("broom")
library("tidyverse")
ratings <- read_csv("GuiltJudgements.csv")

```
```{r T2}
lates <- ratings %>% filter(Evidence == "Middle") %>%
  select(Participant, Evidence, "8", "9") %>%
  rename("Eight" = `8`, "Nine" = `9`) %>% 
  pivot_longer(cols = c("Eight", "Nine"),
               names_to = "Timepoint",
               values_to = "GuiltRating")

```

```{r T3}
##Histogram
lates %>% ggplot(aes(x = GuiltRating, fill = Timepoint)) + 
  geom_histogram(binwidth = 1) + 
  facet_wrap(~ Timepoint) +
  labs(x = "GuiltRating", y = NULL) +
  guides(fill = "none") +
  theme_bw() 
  


```

```{r T4}
##Boxplot
lates %>% ggplot(aes(x = Timepoint, y = GuiltRating, fill = Timepoint)) + 
  geom_boxplot(outliers = TRUE, position = "dodge") +
  scale_y_continuous(breaks = c(1:9)) +
  coord_cartesian(xlim = c(.5, 2.5), ylim = c(1,9), expand = TRUE) +
  labs(x = "GuiltRating", y = NULL) +
  guides(fill = "none") +
  theme_bw() 

```

There are numerous methods such as replacing with a given value or removing the participants. Remember though that this decision, how to deal with outliers, and any deviation from normality, should be considered and written down in advance as part of your preregistration protocol.

```{r T5}
#Violin_boxplot_jitters
lates %>% ggplot(aes(x = Timepoint, y = GuiltRating, fill = Timepoint)) + 
  geom_violin(alpha = 0.2) + 
  geom_jitter(aes(fill = Timepoint), width = 0.1, alpha = 0.2) +
  geom_boxplot(outliers = TRUE, position = "dodge", width = 0.5, alpha = 0.7) +
  scale_y_continuous(breaks = c(1:9)) +
  coord_cartesian(xlim = c(.5, 2.5), ylim = c(1,9), expand = TRUE) +
  labs(x = "GuiltRating", y = NULL) +
  guides(fill = "none") +
  theme_bw() 

##violin_boxplot_difference
lates %>% 
  spread(Timepoint, GuiltRating) %>%
  mutate(diff = Nine - Eight) %>%
  ggplot(aes(x = Evidence, y = diff)) +
  geom_violin() +
  geom_boxplot(fill = "red", 
               width = .5, 
               alpha = .1, 
               outlier.colour = "red") +
  geom_jitter(color = "blue", 
              width = .1, 
              shape = 4) + 
  theme_classic()
```
 
### A violin-boxplot showing the distribution of the scores of the difference between the Thirteen and Twelve conditions. Individual participant data show as blue stars. Positive values would indicate that the rating in the Thirteen condition is higher than the rating in the Twelve condition. Outliers will show as red circles.


```{r T6}
## Descriptive statistics including mean,sd,se,n, and CIs
descriptives <- lates %>% group_by(Timepoint) %>% summarise(n = n(), 
                                                            mean = mean(GuiltRating),
                                                            sd = sd(GuiltRating),
                                                            se = sd / sqrt(n), 
                                                            LowerCI = mean - 1.96 * se,
                                                            UpperCI = mean + 1.96 * se
                                                            )

```

```{r T7}
descriptives %>% ggplot(aes(x = Timepoint, y = mean, fill = Timepoint)) +
  geom_col(position = "dodge") + 
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI), width = 0.1) +
  coord_cartesian(ylim = c(1,9), xlim = c(0.5,2.5)) +
  guides(fill = "none") +
  theme_bw()

###Alternative to T7
ggplot(descriptives, aes(x = Timepoint, y = mean, fill = Timepoint)) + 
  geom_col(colour = "black") +
  scale_fill_manual(values=c("#999000", "#000999")) +
  scale_x_discrete(limits = c("Eight","Nine")) +
  labs(x = "Timepoint of Evidence", y = "GuiltRating") +
  guides(fill="none") +
  geom_errorbar(aes(ymin = LowerCI, ymax = UpperCI),
                position = "dodge", width = .15) +
  scale_y_continuous(breaks = c(1:9), limits = c(0,9)) +
  coord_cartesian(ylim = c(1,9), xlim = c(0.5,2.5), expand = FALSE) +
  theme_classic()
### Alternative to T7
ggplot(descriptives, aes(x = Timepoint, y = mean, fill = Timepoint)) + 
  geom_pointrange(aes(ymin = LowerCI, ymax = UpperCI))+
  scale_x_discrete(limits = c("Eight","Nine")) +
  labs(x = "Timepoint of Evidence", y = "GuiltRating") +
  guides(fill="none")+
  scale_y_continuous(breaks = c(1:9), limits = c(0,9)) +
  coord_cartesian(ylim = c(1,9), xlim = c(0.5,2.5), expand = FALSE) +
  theme_bw()

```

```{r T8}
results <- t.test(lates %>% filter(Timepoint == "Eight") %>% pull(GuiltRating),
                         lates %>% filter(Timepoint == "Nine") %>% pull(GuiltRating),
                            paired = TRUE) %>% tidy()

```

The conf.low and conf.high values are the 95% Confidence Intervals for the mean difference between the two conditions. We haven’t included them in the write-up here but you could do. This could be written as something like, “there was a difference between the two groups (M = -1.76, 95% CI = [-2.19, -1.33])”.


 "A paired-samples t-test was ran to compare the change in guilt ratings before (M = 5.8, SD = 1.5) and after (M = 4.04, SD = 1.93) the crucial evidence was heard. A significant difference was found (t(74) = 8.23, p = 4.7113406^{-12}) with Timepoint 13 having an average rating 1.76 units lower than Timepoint 12. This tells us that the critical evidence did have an influence on the rating of guilt by jury members."
