---
title: "Chapter 9 Correlations: Keeping the Wealthy Wealthy with Correlations"
author: "Mohammad Pourabbasian"
output: html_document
---

```{r setup, include=FALSE}
## DO NOT DELETE THIS CHUNK OR ALTER ANY OF THE LINES WITHIN THIS CHUNK!
knitr::opts_chunk$set(echo = TRUE)
```


# Let's begin!

## Task 1A: Load add-on packages

```{r T2101A}
## To do: Bring in add on packages here
library("broom")
library("tidyverse")


```

## Task 1B: Load the data

    
```{r T2101B}
dat1 <- read_csv("Dawtry Sutton and Sibley 2015 Study 1a.csv")
```

## Task 2: Selecting the necessary columns

There are a lot of columns which you can explore later at your own leisure. For now, today, we are only interested in the ones relevant to our analysis looking at age, fairness and satisfaction of the system, and redistribution of wealth. 


```{r T2102}
dat2 <- dat1 %>% select(age, redist1, redist2, redist3, redist4, fairness, satisfaction)
```

## Task 3: Satisfaction and Fairness measure (Sat_and_Far)

We have two scales relating to fairness and satisfaction but when we run the correlation later we will need one column that captures both measures. We want to create a new variable in our data that is a composite measure of fairness and satisfaction - this we will call `Sat_and_Far`. 

* Replace the `NULL` in the `T2103` code chunk with code that will mutate a new column called `Sat_and_Far` onto the data in `dat2` (watching exact spelling and capitalisation) where values in that column represent the average of the values in the satisfaction and fairness columns for each participant. For example, if a person scores 3 on satisfaction and 1 on fairness, they would have an Sat_and_Far score of 2. Store the output as a tibble in `dat3`.


```{r T2103}
dat3 <- dat2 %>% mutate(Sat_and_Far = (satisfaction + fairness) / 2)
```

## Task 4: Recoding redist3

Similarly, we now want to create one measure related to support for redistribution that is made up of the average of the relevant scales: redist1, redist2, redist3 and redist4.  However, the redist3 scale is negatively scored - meaning that a 1 on that scale would score as a 6 on other scales. 


```{r T2104}
dat4 <- dat3 %>% mutate(redist3_rcd = recode(redist3, "1" = 6, "2" = 5, "3" = 4, "4" = 3, "5"= 2, "6" = 1))
``` 

## Task 5: Recoding redist4

Likewise the column `redist4` is also negatively scored. We will have to repeat the steps of Task 4 but this time we will do so for the redist4 variable. 


```{r T2105}
dat5 <- dat4 %>% mutate(redist4_rcd = recode(redist4, "1" = 6, "2" = 5, "3" = 4, "4" = 3, "5"= 2, "6" = 1))
```

## Task 6: Support for Redistribution (Sup4R)

Now we want to create a single variable within our data that is a composite measure of the four correctly coded redistribution variables (redist1, redist2, redist3_rcd, and redist4_rcd) - we will call this measure `Sup4R` which is short for Support for Redistribution. 


```{r T2106}
dat6 <- dat5 %>% mutate(Sup4R = (redist1 + redist2 + redist3_rcd + redist4_rcd) / 4)
```

## Task 7: Keeping only the necessary columns


```{r T2107}
dat7 <- dat6 %>% select(Sup4R, Sat_and_Far, age)
```

## Task 8: The descriptive measures


```{r T2108}
desc <- dat7 %>% summarise(Npps = n(),
                           Mage = mean(age, na.rm = TRUE),
                           SDage = sd(age, na.rm = TRUE))
library("knitr")
kable(desc, align = "c")
```

## Task 9: The Scatterplot


```{r T2109}
# to do: exactly replicate the figure shown
dat7 %>% ggplot(aes(x = Sat_and_Far, y = Sup4R, color = "red")) + 
  geom_point(shape = 3) + 
  geom_smooth(method = "lm", se = FALSE, color = "blue") + 
  labs(x = "Fairness and Satisfaction",
       y = "Support for Redistribution") + 
  coord_cartesian(xlim = c(1,9),
                  ylim = c(1,6)) + 
  scale_x_continuous(breaks = c(1:9)) + 
  scale_y_continuous(breaks = c(1:6)) +
  guides(color = "none") +
  theme_classic()

```

## Task 10: The correlation


```{r T2110}
mods <- cor.test(dat7$Sat_and_Far, dat7$Sup4R, alternative = "two.sided") %>% tidy()
```

## Task 11: The interpretation

305 participants (mean age = 37.4 years, sd = 12.04 years) were measured on their views regarding distribution of wealth. A Pearson's product-moment correlation was run comparing the composite measures of Fairness and Satisfaction (Sat_and_Far) against Satisfaction for Redistribution (Sup4R) and found a strong significant negative correlation between the two variables, r(303) = -.7, p < .001. As such, the analysis would suggest that as people's perceived fairness of the system increases their support for the redistribution of wealth decreases.


*Finished*