---
title: "One-Way ANOVA"
author: "Mohammad Pourabbasian"
date: "2025-04-01"
output: html_document
---

```{r}
#Setup
library (pwr)
library(lsr)
library(car)
library(broom)
library(afex)
library(emmeans)
library(performance)
library(tidyverse)
dat <- read_csv("James_Holmes_Expt 2_DATA.csv") %>% mutate(subject = row_number())
```
```{r}
#Data Wrangling
#select and rename columns
dat2 <- dat %>% select(subject, Condition, Days_One_to_Seven_Image_Based_Intrusions_in_Intrusion_Diary) %>% rename(intrusions = Days_One_to_Seven_Image_Based_Intrusions_in_Intrusion_Diary)
#recode Condition
dat2 <- dat2 %>% mutate(Condition = as.factor(Condition))
```

```{r}
#Create summary statistics
sum_dat <- dat2 %>% group_by(Condition) %>% summarise(mean = mean(intrusions),
                                                      sd = sd(intrusions),
                                                      se = (sd / n()))
```

```{r}
#Visualisation

dat2 %>% ggplot(aes(x = Condition, y = intrusions, fill = Condition)) + 
  geom_violin(trim = FALSE, alpha = .5) + 
  geom_boxplot(position = "dodge", width = .2) + 
  scale_x_discrete(labels = c("No-task control", "Reactivation plus Tetris", "Tetris only", "Reactivation only")) +
  guides(fill = "none") +
  theme_bw()
```

```{r}
#Bar plot of instrusions by condition
ggplot(sum_dat, aes(x = Condition, y = mean, fill = Condition))+
  stat_summary(fun = "mean", geom = "bar", show.legend = FALSE)+
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.25)+
  scale_y_continuous(limits = c(0,7), 
                     breaks = c(0,1,2,3,4,5,6,7), 
                     name = "Intrusive-Memory Frequency (Mean for the Week")+
  scale_x_discrete(labels = c("No-task control", "Reactivation plus Tetris", "Tetris only", "Reactivation only"))
```
```{r}
#running anova
mod <- aov_ez(id = "subject", # the column containing the subject IDs
              dv = "intrusions", # the dependent variable
              between = "Condition", # the between-subject variable
              es = "pes", # sets effect size to partial eta-squared
              type = 3, # this affects how the sum of squares is calculated, set this to 3
              include_aov = TRUE,
              data = dat2)
anova(mod)
mod_output <- (mod$anova_table) %>% tidy()
```
```{r}
#Assumption check
qqPlot(mod$aov$residuals)
shapiro <- shapiro.test(mod$aov$residuals) %>% #run the test
  tidy() %>% # tidy the output
  mutate(p.value = round(p.value, digits = 3)) # overwrite the p-value with one rounded to 3 decimal places
test_levene(mod) #check for homogeneity of vatiance
```

##Note  
 Well, Field et al. (2009) say that if the sample sizes for each group are equal then ANOVA is robust to violations of both normality and of homogeneity of variance. 

```{r}
#Post-hoc tests
dat2 %>%
  filter(Condition %in% c("1", "2")) %>%
 droplevels() %>%
  t.test(intrusions ~ Condition, data = .)
#correction for multiple comparisons
mod_pairwise <-emmeans(mod, pairwise ~ Condition, adjust = "bonferroni")
mod_contrasts <- mod_pairwise$contrasts %>% tidy()
```

```{r}
#Power Analysis
pwr.anova.test(k = 4, f = .4, sig.level = .05, power = .8)
```
```{r}
#calculating cohen's d for each pairwise comparison
d_1_2 <- cohensD(intrusions ~ Condition, 
                 data = filter(dat2, Condition %in% c(1,2)) %>% 
                   droplevels())
d_1_3 <- cohensD(intrusions ~ Condition, 
                 data = filter(dat2, Condition %in% c(1,3)) %>%
                   droplevels()) 
d_1_4 <- cohensD(intrusions ~ Condition, 
                 data = filter(dat2, Condition %in% c(1,4)) %>%
                   droplevels())
d_2_3 <- cohensD(intrusions ~ Condition, 
                 data = filter(dat2, Condition %in% c(2,3)) %>% 
                   droplevels())
d_2_4 <- cohensD(intrusions ~ Condition, 
                 data = filter(dat2, Condition %in% c(2,4)) %>% 
                   droplevels())
d_3_4 <- cohensD(intrusions ~ Condition, 
                 data = filter(dat2, Condition %in% c(3,4)) %>%
                   droplevels())
pairwise_ds <- c(d_1_2,d_1_3,d_1_4,d_2_3,d_2_4,d_3_4)
mod_contrasts <- mod_contrasts %>%
  mutate(eff_size = pairwise_ds)
```

##Report  

Second, and critically, for the 7-day diary postintervention, there was a significant difference between groups in overall intrusion frequency in daily life, F(`r mod_output$num.Df`, `r mod_output$den.Df`) = `r mod_output$statistic %>% round(2)`, p = `r mod_output$p.value %>% round(3)`, ηp2 = .`r mod_output$ges %>% round(2)`. Planned comparisons demonstrated that relative to the no-task control group, only those in the reactivation-plus-Tetris group, t(`r mod_contrasts$df[1]`) = `r mod_contrasts$statistic[1] %>% round(2)`, p = `r mod_contrasts$adj.p.value[1] %>% round(2)`, d = `r mod_contrasts$eff_size[1] %>% round(2)`, experienced significantly fewer intrusive memories; this finding replicated Experiment 1. The reactivation-plus-Tetris group had significantly fewer intrusive thoughts than the reactivation-only group, t(`r mod_contrasts$df[5]`) = `r mod_contrasts$statistic[5] %>% round(2)`, p = `r mod_contrasts$adj.p.value[5] %>% round(2)`, d = `r mod_contrasts$eff_size[5] %>% round(2)`. Further, there were no significant differences between the reactivation-plus-Tetris group and the Tetris-only group, t(`r mod_contrasts$df[4]`) = `r mod_contrasts$statistic[4] %>% round(2)`, p = `r mod_contrasts$adj.p.value[4] %>% round(2)`, d = `r mod_contrasts$eff_size[4] %>% round(2)`, the no-task control group and the reactivation-only group, t(`r mod_contrasts$df[3]`) = `r mod_contrasts$statistic[3] %>% round(2)`, p = `r mod_contrasts$adj.p.value[3] %>% round(2)`, or between the no-task control group and the Tetris-only group, t(`r mod_contrasts$df[2]`) = `r mod_contrasts$statistic[2] %>% round(2)`, p = `r mod_contrasts$adj.p.value[2] %>% round(2)`



